Books and Babies: An Analysis of the Relationship between Female Literacy Rate and Fertility Rate in South Asia (2000-2020)

### 2024-04-18 paper/paper.qmd
update paper.wmd, upload usage3.txt

>>>>

```{r, results='asis'}
#| label: tbl-model2
#| tbl-cap: "Summary of the linear regression model"
#| echo: false
#| warning: false
library(knitr)

# Load the data from the RDS file
loaded_model <- readRDS(here::here("models/linear_model.rds"))

# Extract coefficients and their standard errors
coefficients <- round(coef(loaded_model), 3)
standard_errors <- round(summary(loaded_model)$coefficients[, "Std. Error"], 3)

# Create a data frame
model_data <- data.frame(Coefficients = coefficients, Standard_Error = standard_errors)

# Render the data frame as a table using kable
kable(model_data, format = "markdown")

# Extract number of observations, R-squared value, and additional model metrics
n_obs <- length(residuals(loaded_model))
r_squared <- summary(loaded_model)$r.squared
r_squared_adj <- summary(loaded_model)$adj.r.squared
aic <- AIC(loaded_model)
bic <- BIC(loaded_model)
log_likelihood <- logLik(loaded_model)
rmse <- sqrt(mean(residuals(loaded_model)^2))

# Create a data frame for the model metrics
model_metrics <- data.frame(
  Metric = c("Num.Obs.", "R2", "R2 Adj.", "AIC", "BIC", "Log.Lik.", "RMSE"),
  Value = c(n_obs, round(r_squared, 3), round(r_squared_adj, 3), aic, bic, log_likelihood, round(rmse, 2))
)

# Render the data frame as a table using kable
kable(model_metrics, format = "markdown")
